On the computational complexity of detecting possibilistic locality

### 2017-06-19 paper.tex
More work on background. Mentioned the possibilistic collapse and added referencing to Abramsky and to Mansfield & Barbosa.

@@

>>>>

This table of probabilities can be converted into a table of possibilities via a \emph{possibilistic collapse}, explored by Abramsky \cite{Abra2013-2}, and by Mansfield and Barbosa \cite{Mans2014}. We apply to the event probabilities, the mapping
\begin{equation}
f(p)=\begin{cases} 1 \quad p\neq 0 \\ 0 \quad p=0, \end{cases}
\end{equation}
which acts as a homomorphism between the normal probability semiring $\mathbb{R}_+$, and the Boolean semiring on $\{0,1\}$. The result of such a collapse applied to the CHSH scenario is also presented in Figure \ref{CHSH}.

%Need to add: what is no-signalling. What does it meant to be quantumly accessible? What's the complexity of finding out if one is?

@@

%Give specific decomposition of a deterministic grid.
